
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4 in,right=0.4 in,bottom=0.4 in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{AKHIL SHETTY M} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+91 895 122 3864 \\ Mangaluru, Karnataka}
\address{\href{mailto:akhilshettym2003@gmail.com}{\textcolor{black}{akhilshettym@gmail.com}} \\ \href{https://www.linkedin.com/in/akhilshettym/}{\textcolor{black}{linkedin.com/in/akhilshettym}} \\ \href{https://www.github.com/akhilshettyym}{\textcolor{black}{github.com/akhilshettyym}}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{
Computer Science undergraduate with a strong academic foundation and a passion for technology. Eager to launch my career and contribute to innovative projects. Possess a solid understanding of algorithms, data structures, software development principles, and graphic designing. Excited to apply my knowledge and skills to real-world
}

\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Bachelor of Engineering}, St. Joseph Engineering College, Mangaluru \hfill {2021 - 2025(expected)}\\
Computer Science and Engineering, CGPA - 8.42/10

{\bf Higher Secondary}, Boscoss PU College, Mangaluru \hfill {2019 - 2021}\\
PCMB, Percentage - 95.17\%

{\bf High School}, Canara High School, Urwa, Mangaluru \hfill {2009 - 2019}\\
SSLC Percentage - 88.84\%
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Technical Skills & C, Java, Python, HTML, CSS, JS, MySQL, Matlab, Adobe animate, SolidWorks, Ansys, Git.
\\
Soft Skills & Adaptability, Interpersonal Communication, Punctual, Time Management\\
% Other Skills & UAV Piloting, RC Aircraft and Drone Fabrication\\
\end{tabular}
\end{rSection}

\begin{rSection}{INTERNSHIPS}

\textbf{Graphic Designing Intern} \hfill Oct 2023 - Nov 2023\\
Karanji Infotech Pvt. Ltd. \hfill \textit{Mangaluru, Karnataka}
 \begin{itemize}
    \itemsep -3pt {} 
    %  \item Carried out 4-week internship in the web development domain
     \item Created visually appealing graphics for marketing campaigns, including brochures, posters, and social media content.
    \item Utilized industry-standard design software such as Adobe Creative Suite(Animate,(Basics Blender)) to create and edit designs, Worked closely with team members to understand project requirements and deliver designs. 
 \end{itemize}
 


\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\begin{itemize}
\item \textbf{Pet Shop}{, An innovative web platform designed to streamline the process of purchasing pet supplies and services. Customers can easily browse products and place orders without the need to visit the pet store.}
% \textbf{Github repository: }\href{https://github.com/AbhikSalian/tailor-database}{\textcolor{black}{https://github.com/AbhikSalian/tailor-database}}}
\item \textbf{WiFi based Intelligent Parking Space}{, Implemented using ESP8266 WiFi Module and Blynk IoT, which manages the empty parking slots in enclosed parking spaces by directing the incoming cars to those slots.}
% \textbf{Github repository: }\href{https://github.com/AbhikSalian/smart-parking-system}{\textcolor{black}{https://github.com/AbhikSalian/smart-parking-system}}}
% \textbf{Github repository: }\href{https://github.com/AbhikSalian/animal-tracking-system}{\textcolor{black}{https://github.com/AbhikSalian/animal-tracking-system}}}
\end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Certificates} 
    \begin{itemize}
        \item \textbf{Python Course} \hfill Sept 2023\\
        Python Complete Course for Beginners provided comprehensive training in Python programming.
        \item \textbf{Adobe animate} \hfill Nov 2023\\
        A 10-hour comprehensive course on Adobe Animate, covering key features and tools to create interactive content.
    \end{itemize}
    
    
    \end{rSection}
    \begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}
    \item 	\textbf{Cultural Committee Student Coordinator} at \textbf{SJEC}, Cultural Committee Student Coordinator of the CSE Department, responsible for organizing and managing cultural events and activities within the department.
    \item	\textbf{Volunteer} at \textbf{TedX-SJEC}, TEDx Design Team Volunteer, responsible for creating engaging visual content.

\end{itemize}


\end{rSection}

\begin{rSection}{Achievements} 
    \begin{itemize}
        \item 	\textbf{First place} at \textbf{Tiara, lines and shades} 
 a national level techno-cultural fest held at SJEC, 2023, 2024.
    
    \end{itemize}
    
    
    \end{rSection}


\end{document}